Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-04-16 manuscript/manuscript.tex
responded to some comments

Despite its widespread use, the KS test can be 
misapplied when its foundational assumptions are overlooked. The KS test 
assumes the data are independently and identically distributed (i.i.d.) and 
\jy{no defining acronyms that are not used later}
that the hypothesized distribution is continuous and fully specified without 
the need for parameter estimation. \citet{zeimbekakis2022misuses} examines
common misapplications of the one-sample KS test. One notable inappropriate
use is when the hypothesized distribution contains unspecified parameters.
In this case, the tests are generally constructed by substituting the unknown
parameters by their estimates, and the asymptotic null distribution of
the test statistic may depend in a complex way on the unknown parameters.
The problem of unspecified parameters can be handled by a parametric
bootstrap, where bootstrap samples of the test statistics are constructed from
samples generated from the fitted hypothesized distribution.
Alternatively, \citet{babu2004goodness} address this issue through a
non-parametric bootstrap method that corrects the bias in the asymptotic null
distribution.

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with Kendall's
$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence as it does not vary between two different 
marginal distributions.
To generate the samples to which our
method would be applied, we simulated a time series $W_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation*}
W_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: 
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_t$ by
\begin{equation*}
X_t = F^{-1}[\Phi(W_t)],
\end{equation*}
\jy{define $\Phi$}
\jy{The language issues are more than I expected. Please do a careful proofread,
  now that you are more experienced.}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
distribution.
Then we generated a marginal gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution.
After the transformation
to the marginal gamma distribution, the autocorrelations are $\{-0.884, 
-0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}$.

@@

\jy{Remove the white space in the pdf figures. Could put the zoomed version in
  the same figure.}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width = \textwidth]{figures/zoom_normal}
  \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:normal} zoomed in to 
  probabilities between 0 and  0.1.}
  \label{fig:zoom_normal}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/zoom_gamma}
  \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:gamma} zoomed in to 
  probabilities between 0 and 0.1.}
  \label{fig:zoom_gamma}
\end{figure}

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
although the extent to which the p-values appear to be 
completely aligned with the line
in the Q-Q plots is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in the Q-Q plots, even
in Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high. Additionally, performance generally seems
better for negative $\tau$ values versus positive $\tau$ values of the same
strength. Results are very similar for normal and gamma margins.
\jy{Summarize findings in bullet points before forming text.}

Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
\jy{Not true from the plots.}
uniformly distributed. This is an indication that our method 
holds its size and that we can expect the probability
of a type 1 error to be the significance level $\alpha$.

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. If the test
is indeed powerful, we would ideally want $\beta$ \jy{beta has been
  used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
  is false.}
to be 0, but we
expect it to be generally low. Again, we must try the method with different
marginal distributions to ensure that it is robust.
We would then expect the distribution of p-values to be non-uniform, and the 
rate \jy{Does not sound right. What is $\alpha$?}
of $\#P < \alpha$ to be high, meaning a higher density of low p-values.

@@

While differences in p-values among different methods are expected, our analysis
reveals numerous instances where conclusions at the 0.05 significance level
using our method differ from those obtained using the methods proposed by
\citet{babu2004goodness} and \citet{zeimbekakis2022misuses}.
\jy{I don't like one-sentence paragraphs.}

For example, when assessing the S\&P 500 series, our method fails to reject the
hypothesis that the series follows a Student's $t$ distribution with degrees of
freedom $v = 5$ with a p-value of 0.061. In contrast, Babu and Sen's method
yields a p-value of 0.0222, and Zeimbekakis et al.'s method yields a p-value of
0.0141. Although such differences are not guaranteed, this
instance highlights a disagreement in conclusions among methods for the S\&P 500
index.

@@

We have also 
demonstrated possible applications of this method to financial data.
\jy{don't astrophie citet; let alone citep}
Through comparison with \citep{babu2004goodness}'s non-parametric
bootstrap bias correction and \citet{zeimbekakis2022misuses}'s parametric
bootstrap method, we have underscored the importance of accounting for serial
dependence in choosing an appropriate methodology.
This method holds relevance for studies aiming to assess if a serially dependent
time series adheres to a hypothesized distribution in scenarios where parameters
are unknown or unspecified. Future studies could investigate
\jy{Too vague.}
the method's performance on different marginal distributions and
different dependence structures. Additionally, one could propose a 
similar method
for comparing two serially dependent methods. One could also apply the method
showcased
in this paper to fields like earthquake prediction and astronomy.

>>>>

Despite its widespread use, the KS test can be 
misapplied when its foundational assumptions are overlooked. The KS test 
assumes the data are independently and identically distributed and 
that the hypothesized distribution is continuous and fully specified without 
the need for parameter estimation. \citet{zeimbekakis2022misuses} examines
common misapplications of the one-sample KS test. One notable inappropriate
use is when the hypothesized distribution contains unspecified parameters.
In this case, the tests are generally constructed by substituting the unknown
parameters by their estimates, and the asymptotic null distribution of
the test statistic may depend in a complex way on the unknown parameters.
The problem of unspecified parameters can be handled by a parametric
bootstrap, where bootstrap samples of the test statistics are constructed from
samples generated from the fitted hypothesized distribution.
Alternatively, \citet{babu2004goodness} address this issue through a
non-parametric bootstrap method that corrects the bias in the asymptotic null
distribution.

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with Kendall's
$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence as it does not vary between two different 
marginal distributions.
To generate the samples to which our
method would be applied, we simulated a time series $W_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation*}
W_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: 
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_t$ by
\begin{equation*}
X_t = F^{-1}[\Phi(W_t)],
\end{equation*}
\jy{define $\Phi$}\mc{addressed}
\jy{The language issues are more than I expected. Please do a careful proofread,
  now that you are more experienced.}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
distribution and $\Phi$ is the distribution function of the standard normal
distribution.
Then we generated a marginal gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution.
After the transformation
to the marginal gamma distribution, the autocorrelations are $\{-0.884, 
-0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}$.

@@

\jy{Remove the white space in the pdf figures. Could put the zoomed version in
  the same figure.}\mc{addressed}

@@

@@

\input{tables/rr_100}

\input{tables/rr_200}

\input{tables/rr_400}

\input{tables/rr_800}

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
although the extent to which the p-values appear to be 
completely aligned with the line
in the Q-Q plots is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in the Q-Q plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high. Additionally, performance generally seems
better for negative $\tau$ values versus positive $\tau$ values of the same
strength. Results are very similar for normal and gamma margins.
\jy{Summarize findings in bullet points before forming text.}

Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
\jy{Not true from the plots.}\mc{addressed}
uniformly distributed as long as the serial dependence is not too high. 
This is an indication that our method 
holds its size for moderate serial dependence levels.
For such cases, we can expect the probability
of a type 1 error to be the significance level $\alpha$.

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. If the test
is indeed powerful, we would ideally want the probability of
rejecting $H_0$ when $H_0$ is false\jy{beta has been
  used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
  is false.}
to be 1, but we
expect it to be generally high. Again, we must try the method with different
marginal distributions to ensure that it is robust.
We would then expect the distribution of p-values to be non-uniform, and the 
rate \jy{Does not sound right. What is $\alpha$?}
of $\#P < \alpha$ to be high, meaning a higher density of low p-values.

@@

While differences in p-values among different methods are expected, our analysis
reveals numerous instances where conclusions at the 0.05 significance level
using our method differ from those obtained using the methods proposed by
\citet{babu2004goodness} and \citet{zeimbekakis2022misuses}.
For example, when assessing the S\&P 500 series, our method fails to reject the
hypothesis that the series follows a Student's $t$ distribution with degrees of
freedom $v = 5$ with a p-value of 0.061. In contrast, Babu and Sen's method
yields a p-value of 0.0222, and Zeimbekakis et al.'s method yields a p-value of
0.0141. Although such differences are not guaranteed, this
instance highlights a disagreement in conclusions among methods for the S\&P 500
index.

@@

We have also 
demonstrated possible applications of this method to financial data.
\jy{don't astrophie citet; let alone citep}\mc{addressed}
Through comparison with the non-parametric
bootstrap bias correction developed by \citet{babu2004goodness}
and the parametric
bootstrap method developed by \citet{zeimbekakis2022misuses}, we have 
underscored the importance of accounting for serial
dependence in choosing an appropriate methodology.
This method holds relevance for studies aiming to assess if a serially dependent
time series adheres to a hypothesized distribution in scenarios where parameters
are unknown or unspecified. Future studies could investigate
\jy{Too vague.}
the method's performance on different marginal distributions and
different dependence structures. Additionally, one could propose a 
similar method
for comparing two serially dependent methods. One could also apply the method
showcased
in this paper to fields like earthquake prediction and astronomy.
